---
title: "Telling Stories with Data - Study"
format: html
editor: visual
include: false
---

## Reproducible workflows

### Github

To set up a new project, here are the following steps:

1.  Create new repository in Github

    1.  Check "Initialize this repository with a README"
    2.  Change "Add.gitignore" to R

2.  Copy link to clipboard

3.  Return to RStudio and create a new project

    1.  File -\> New project -\> Version control -\> Git
    2.  Paste URL
    3.  Check "Open in a new session"
    4.  Click "Create Project"

4.  Use a Personal Access Token (PAT) to link our RStudio Workspace with Github

    ```{r}
    install.packages("usethis")

    # set your user name and email
    usethis::use_git_config(user.name = "YourName", user.email = "your@mail.ca")

    # create a personal access token for authentication
    usethis::create_github_token()
    ```

```{=html}
<!-- -->
```
5.  Replace Note with "PAT for Rstudio" and generate token

    ```{r}
    credentials::set_github_pat("YourPAT")
    ```

6.  Maintain using pull, commit, and push

## Running Code

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).
